The guts of the dispRity package

### 2018-03-01 inst/gitbook/05_guts.Rmd
changed scale to rescale

#### `scale.dispRity`
This is the S3 method of `scale` (scaling and/or centring) that can be applied to the disparity data of a `dispRity` object.

@@

## Scaling the same disparity values
head(summary(scale(disparity, scale = TRUE)))

## Scaling and centering:
head(summary(scale(disparity, scale = TRUE, center = TRUE)))
```

>>>>

#### `rescale.dispRity`
This is the modified S3 method for `scale` (scaling and/or centring) that can be applied to the disparity data of a `dispRity` object and can take optional arguments (for example the rescaling by dividing by a maximum value).

@@

## Scaling the same disparity values
head(summary(rescale.dispRity(disparity, scale = TRUE)))

## Scaling and centering:
head(summary(rescale.dispRity(disparity, scale = TRUE, center = TRUE)))

## Rescaling the value by dividing by a maximum value
head(summary(rescale.dispRity(disparity, max = 10)))
```
